---
title: "Prediction using Supervised ML"
author: "Srimurari"
---

###                                               The Sparks Foundation

####                                          Task 1 - Prediction using Supervised ML

####                                      Domain - Data Science and Business Analytics

#### Objectives

-   Predict the percentage of an student based on the no.of study hours.

-   Predict score if a student studies for 9.25 hrs/day.

Importing the required packages and data set.

```{r}

library(ggplot2)
hs<-read.csv("http://bit.ly/w-data")
```

```{r}
hs

```

```{r}
head(hs)
```

Statistical Description of the Data set.

```{r}
summary(hs)
```

Structure of the data set

```{r}
str(hs)
```

In R, the lm(), or linear model, function can be used to create a simple regression model. For Simple linear regression, Y\~X where Y is dependent variable and X is Independent Variable.A linear model is used to predict the value of an unknown variable based on independent variables.

```{r}
m<-lm(hs$Scores~hs$Hours)
m
```

The lm() returns the slope and intercept of the regression line, using those we can find predict the actual values.

```{r}
Scores1<-predict(m)
Scores1
```

The predicted values are added to the data set.

```{r}
hs<-cbind(hs,Scores1)
hs
```

Using ggplot(), we visualize the given data

```{r}
ggplot(hs)+aes(Hours,Scores)+geom_point(color='Red')+geom_smooth(formula=y~x,method=lm,se=TRUE)+
  labs(title='Hours vs Scores',subtitle='TASK1',caption='Prediction using Supervised ML')

```

Predicting the student score when he/she studies for 9.25 hrs/day.

```{r}
x<-coef(m)
intercept<-x[1]
slope<-x[2]
slope*9.25+intercept

```

#### Conclusion - 

So the student will score 93 marks approximately when he/she studies for 9.25 hours per day.
